Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-14 exp1/present2013.tex
fix the effects slide
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@670 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{frame}{Main effects}

\emph{Effects} describe the influence of the levels on the response.

The the \emph{main effect}: For a factor $A$ with two levels, we let
$a_1$ and $a_2$ be the average response of all $2^{n-1}$ measurements
with $A$ at level 1, and 2, respectively.  The main effect of $A$ is
then defined as $a_2 - a_1$.

For example:

For each implementation, average all the responses. Then, the main
effect of the implementation is the difference between them.

\begin{frame}{Interaction effects}

\emph{Interaction effects} for two factors $AB$ are defined
by comparing averages for equal versus non-equal levels of $A$ and
$B$.

For example:

For each implementation, find the averages for each dataset size, the
interaction effect is % TODO: Clear example.

In practice, Quite Easily Done using linear regression.
\end{frame}
\note{Interaction effects may be complex, like one implementation is
  better on CONSTRUCT queries, on small datasets}
\note{We still need to understand which effects are important and
  significant, we do that in the discussion of our experiment}

>>>>

\begin{frame}{Effects}

\Larger 
\emph{Effects} describe the influence of the levels on the response.
\normalsize

\begin{itemize}
\item Similarities to regression.
\item \emph{Main effects} consider the factors on their own.
\item \emph{Interaction effects} consider factors given levels of
  other factors.
\item In practice done with linear regression routines.
\end{itemize}

\end{frame}
\note{Interaction effects may be complex, like one implementation is
  better on CONSTRUCT queries, on small datasets}
\note{We still need to understand which effects are important and
  significant, we do that in the discussion of our experiment}
